Characterizing the response of subarctic European vegetation to key environmental variables for land surface modeling of ozone pollution and risk assessment

### 2021-10-15 VegOzone.tex
Checked author contrib

\authorcontribution{All authors contributed to framing this research article, writing, and conclusions. SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV has performed the on-site observation of vegetation damage induced by ozone, provided advice on plant physiological processes, collected exisiting literature on subarctic vegetation, contributed significantly to framing and proof reading this research article. LE has contributed with expertize in $\mathrm{DO_3SE}$ modeling and development of the PDF-based temperature acclimation assessment. CO has collected PFT parameters from the literature, performed all $\mathrm{DO_3SE}$ simulations and validation. AE contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with an assessment of the 2018 meteorological conditions and writing the proposal for founding this project. TB gave valuable guidance in a broader research sense.} %% this section is mandatory

>>>>

\authorcontribution{All authors contributed to framing this research article, writing, and conclusions. SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV has conducted the on-site observation of vegetation damage induced by ozone, provided advice on plant physiological processes, collected existing literature on subarctic vegetation, contributed significantly to framing and proofreading this research article. LE has contributed with expertise in $\mathrm{DO_3SE}$ modeling and development of the PDF-based temperature acclimation assessment. CO has collected PFT parameters from the literature, performed all $\mathrm{DO_3SE}$ simulations and validation. AE contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with an assessment of the 2018 meteorological conditions and writing the proposal for funding this project. TB gave valuable guidance in a broader research sense.} %% this section is mandatory
